### 2014-05-21 todo.tex
update todo

  \begin{itemize}
    \item Menger/Rothberger properties and games results
      \begin{itemize}
        \item Is there a slick characterization of $F\kmarkwin{2}\mengame{X}$ for regular/general spaces?
        \item Is $F\uparrow_{?}\mengame{X}$ or $F\uparrow_{?}\rothgame{X}$ a hereditary property under closed subsets for any type of limited information? (The Menger property is; is Rothberger?)
        \item Investigate Markov strategies for $S$ in $\rothgame{X}$ or $P$ in $\altrothgame{X}$.
        \item $S\kmarkwin{2}\rothgame{X}\Leftrightarrow S\kmarkwin{k}\rothgame{X}$?
        \item $S\kmarkwin{2}\rothgame{\oneptcomp{\omega_1}}$ or $S\kmarkwin{2}\rothgame{\oneptlind{\omega_1}}$?
        \item $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$?
        \item Would Lindelof scattered spaces have a $2$-Markov strategy in the Menger game?
      \end{itemize}
    \item Filling games
      \begin{itemize}
        \item Show/disprove $F\ktactwin{3}\sfillgame{J}$ implies $F\kmarkwin{3}\fillgame{J}$.
        \item Show/disprove $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ implies $F\kmarkwin{2}\kfillgame{\kappa}$.
      \end{itemize}
    \item Search for a class of spaces where $K\ktactwin{2}\lfkpgame{X}$ characterizes metacompact (aka implies $K\tactwin\lfkpgame{X}$)
      \begin{itemize}
        \item Investigate the ladder space suggested by G.
        \item Try zero-dimensional.
      \end{itemize}
    \item Proximity Game
      \begin{itemize}
        \item Does predetermined strategy for D on abs. proxmial space, imply predetermined strategy for O in con(X,H) for H compact?
        \item Is proximal game properties preserved under perfect maps? Or, compact proximal preserved under continuous.
        \item Does the one-point compactification of ladder omega_1 space have Markov strategy? (Try ladder space where
              nth rung is limit+n => is a Moore space and has G_delta diagonal)
        \item Does the Michael line have a predetermined/Markov strategy?
        \item Uniformly locally compact plus predtermiend implies metrizable unifomrity.
      \end{itemize}
  \end{itemize}
\end{document}

>>>>

  \begin{itemize}
    \item Menger/Rothberger properties and games results
      \begin{itemize}
        \item Is there a slick characterization of $F\kmarkwin{2}\mengame{X}$ for regular/general spaces?
        \item Is $F\uparrow_{?}\mengame{X}$ or $F\uparrow_{?}\rothgame{X}$ a hereditary property under closed subsets for any type of limited information? (The Menger property is; is Rothberger?)
        \item Investigate Markov strategies for $S$ in $\rothgame{X}$ or $P$ in $\altrothgame{X}$.
        \item $S\kmarkwin{2}\rothgame{X}\Leftrightarrow S\kmarkwin{k}\rothgame{X}$?
        \item $S\kmarkwin{2}\rothgame{\oneptcomp{\omega_1}}$ or $S\kmarkwin{2}\rothgame{\oneptlind{\omega_1}}$?
        \item $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$?
        \item Would Lindelof scattered spaces have a $2$-Markov strategy in the Menger game?
      \end{itemize}
    \item Filling games
      \begin{itemize}
        \item Show/disprove $F\ktactwin{3}\sfillgame{J}$ implies $F\kmarkwin{3}\fillgame{J}$.
        \item Show/disprove $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ implies $F\kmarkwin{2}\kfillgame{\kappa}$.
      \end{itemize}
    \item Search for a class of spaces where $K\ktactwin{2}\lfkpgame{X}$ characterizes metacompact (aka implies $K\tactwin\lfkpgame{X}$)
      \begin{itemize}
        \item Investigate the ladder space suggested by G.
        \item Try zero-dimensional.
      \end{itemize}
    \item Proximity Game
      \begin{itemize}
        \item Does predetermined strategy for D on abs. proxmial space, imply predetermined strategy for O in con(X,H) for H compact?
        \item Is proximal game properties preserved under perfect maps? Or, compact proximal preserved under continuous.
        \item Does the one-point compactification of ladder $\omega_1$ space have Markov strategy? (Try ladder space where
              nth rung is limit+n $\Rightarrow$ is a Moore space and has $G_\delta$ diagonal)
        \item Does the Michael line have a predetermined/Markov strategy?
        \item Uniformly locally compact plus predtermiend implies metrizable unifomrity.
        \item What about Bernstein set?
        \item Is there a non-normal ladder $X$ with $\pl P\not\win\proxgame{X}$?
          \begin{itemize}
            \item Diamond implies there exists a ladder such that for any
                  uncountable subset of successors, the rungs for a limit is
                  contained.
            \item So assume diamond, or maybe just CH.
          \end{itemize}
      \end{itemize}
  \end{itemize}
\end{document}
